---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nuyina.underway

<!-- badges: start -->
<!-- badges: end -->

The goal of nuyina.underway is to get the Nuyina underway data. 



This layer `underway:nuyina_underway` is published at this address, but we regularly cache this in convenient tabular form and only request from the service what data is new. 

'https://data.aad.gov.au/geoserver/ows?service=WFS&acceptversions=2.0.0&request=GetCapabilities'. 

The cache lives here, and can be read at any time with Parquet readers (Arrow, GDAL, etc): 

'https://github.com/mdsumner/uwy.new/releases/download/v0.0.1/nuyina_underway.parquet'

## Installation

You can install the development version of nuyina.underway like so:

``` r
remotes::install_github("mdsumner/nuyina.underway")
```

## Example

This is a basic example. 

```{r example}
library(nuyina.underway)
d <- nuyina_underway() ; print(length(names(d)))
d |> dplyr::select(datetime, longitude, latitude, platform_pitch_fore_up,sea_water_temperature) |> tail()
```


## Code of Conduct
  
Please note that the nuyina.underway project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
